---
title: "Projects"
description: "A live gallery of projects published as GitHub Pages sites — pulled directly from my GitHub account so it stays current as new things go up."
toc: true
toc-depth: 2
format:
  html:
    page-layout: full
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(httr2)
library(jsonlite)
library(dplyr)
library(purrr)
library(htmltools)
library(lubridate)

# Repos that have Pages enabled but aren't worth showcasing
# (templates, abandoned scaffolds, accidental forks, etc.)
exclude <- c(
  "hello-world",
  "github.io",
  "adamdennett_test.github.io",
  "adamdennett.github.io",   # academicpages template – not actively used
  "Week6Practical",
  "starter-academic"
)

# Optional manual category tags by repo name — repos not listed here are "Other"
categories <- list(
  "Brighton & Hove schools"        = c("BH_Schools_2", "BH_Schools_Consultation",
                                       "BH_Secondary_Admissions_Analysis",
                                       "bh_school_choice", "school_attainment_tool"),
  "Local government & policy"      = c("BH_Reoganisation", "council_tax",
                                       "defibrillator-analysis"),
  "Energy & EPC"                   = c("EPC_Analysis_Website", "EPC_Data_Analysis"),
  "Teaching"                       = c("QM", "casa0007_qm", "cartosdsbootcamp",
                                       "casa_demo"),
  "Talks & presentations"          = c("aalto_presentation_2024", "AUM2024"),
  "Maps & explorers"               = c("BrightonRestaurantsMap"),
  "Data resources & methods"       = c("Synthetic-LS-spines", "SIModelling")
)

fetch_repos <- function(user = "adamdennett") {
  req <- request("https://api.github.com/users/") |>
    req_url_path_append(user, "repos") |>
    req_url_query(per_page = 100, type = "owner", sort = "updated") |>
    req_headers("Accept" = "application/vnd.github+json",
                "X-GitHub-Api-Version" = "2022-11-28")
  pat <- Sys.getenv("GITHUB_PAT", unset = Sys.getenv("GITHUB_TOKEN"))
  if (nzchar(pat)) req <- req_auth_bearer_token(req, pat)
  req_perform(req) |> resp_body_json()
}

repos <- fetch_repos()

repo_df <- map_dfr(repos, function(r) {
  tibble(
    name        = r$name,
    description = r$description %||% "",
    language    = r$language %||% "",
    fork        = isTRUE(r$fork),
    archived    = isTRUE(r$archived),
    has_pages   = isTRUE(r$has_pages),
    stars       = r$stargazers_count %||% 0L,
    updated     = as_date(ymd_hms(r$updated_at)),
    repo_url    = r$html_url,
    pages_url   = sprintf("https://adamdennett.github.io/%s/", r$name)
  )
}) |>
  filter(has_pages, !archived, !(name %in% exclude)) |>
  arrange(desc(updated))

# Attach category
cat_lookup <- stack(categories) |>
  setNames(c("name", "category")) |>
  mutate(across(everything(), as.character))
repo_df <- repo_df |>
  left_join(cat_lookup, by = "name") |>
  mutate(category = ifelse(is.na(category), "Other", category))

card <- function(row) {
  div(class = "project-card",
      div(class = "project-card-body",
          h3(class = "project-title",
             a(href = row$pages_url, target = "_blank", row$name)),
          if (nzchar(row$description))
            p(class = "project-desc", row$description)
          else
            p(class = "project-desc project-desc-empty", em("(no description)")),
          div(class = "project-meta",
              if (nzchar(row$language))
                span(class = "badge lang", row$language),
              span(class = "badge date",
                   paste0("Updated ", format(row$updated, "%b %Y"))),
              if (row$stars > 0)
                span(class = "badge stars", paste0("★ ", row$stars)),
              if (row$fork)
                span(class = "badge fork", "fork")
          ),
          div(class = "project-links",
              a(href = row$pages_url, target = "_blank", "Live site →"),
              a(href = row$repo_url,  target = "_blank", "Source")
          )
      )
  )
}

render_section <- function(df, heading) {
  if (nrow(df) == 0) return(NULL)
  tagList(
    h2(heading),
    div(class = "project-grid",
        lapply(split(df, seq_len(nrow(df))), card)
    )
  )
}
```

```{r summary}
htmltools::p(
  class = "project-summary",
  sprintf("%d live project sites across %d categories — sorted within each category by most recent activity.",
          nrow(repo_df),
          length(unique(repo_df$category)))
)
```

```{r render-categories}
#| output: asis
# Preserve the manual category order, with "Other" last
ordered_cats <- c(names(categories), "Other")
ordered_cats <- ordered_cats[ordered_cats %in% unique(repo_df$category)]

sections <- lapply(ordered_cats, function(cat) {
  sub <- repo_df |> filter(category == cat)
  render_section(sub, cat)
})

# Emit inside a pandoc raw-HTML fence so indented child tags don't get
# re-interpreted as Markdown indented code blocks.
cat("\n```{=html}\n")
cat(as.character(htmltools::tagList(sections)))
cat("\n```\n")
```

::: {.callout-tip collapse="true"}
## How this page works

This page is built from a live call to the GitHub API at render time — it lists
every repository under [adamdennett](https://github.com/adamdennett) that has
GitHub Pages enabled, minus a small manual exclude list of templates and
scaffolds. Categories are assigned by name in the setup chunk at the top of
`projects.qmd`; anything uncategorised falls into "Other". Rebuild the site
to refresh.
:::
