---
title: "Publications"
description: "Pulled live from my ORCID record on every render — should always be current."
toc: true
toc-depth: 2
toc-title: "Jump to year"
format:
  html:
    page-layout: full
execute:
  echo: false
  warning: false
  message: false
  freeze: false   # always re-fetch from ORCID
---

```{r setup}
library(httr2)
library(jsonlite)
library(dplyr)
library(purrr)
library(htmltools)
library(stringr)

ORCID <- "0000-0001-8036-0185"

# ---- ORCID API helpers -----------------------------------------------------

orcid_req <- function(url) {
  request(url) |>
    req_headers(Accept = "application/json",
                `User-Agent` = "adamdennett.co.uk publications page")
}

# Fetch the summary list of all works.
works_summary <- orcid_req(sprintf(
  "https://pub.orcid.org/v3.0/%s/works", ORCID
)) |>
  req_perform() |>
  resp_body_json()

groups <- works_summary$group

# ORCID groups duplicate submissions of the same work (same DOI) into one
# group with multiple work-summary entries (one per source — manual,
# CrossRef, Scopus, ...). Pick the first put-code from each group as the
# canonical entry, then fetch its full record (which has authors).
put_codes <- map_chr(groups, ~ as.character(.x$`work-summary`[[1]]$`put-code`))

work_reqs <- map(put_codes, function(pc) {
  orcid_req(sprintf("https://pub.orcid.org/v3.0/%s/work/%s", ORCID, pc))
})

work_resps <- req_perform_parallel(work_reqs, on_error = "continue",
                                   max_active = 8)

# ---- Parse one work record into a tidy row ---------------------------------

parse_work <- function(w) {
  if (is.null(w)) return(NULL)
  title <- w$title$title$value %||% NA_character_
  if (is.na(title) || !nzchar(title)) return(NULL)

  yr <- suppressWarnings(as.integer(
    (w$`publication-date` %||% list())$year$value
  ))

  journal <- (w$`journal-title` %||% list())$value %||% ""

  # External IDs — pull out DOI (preferred) or any other URL
  ext_ids <- (w$`external-ids` %||% list())$`external-id` %||% list()
  doi <- NA_character_
  for (eid in ext_ids) {
    if (identical(eid$`external-id-type`, "doi")) {
      doi <- eid$`external-id-value`; break
    }
  }

  # Work URL (often points at the publisher / DOI landing page)
  work_url <- (w$url %||% list())$value %||% NA_character_

  # Contributors (authors) — credit-name.value is the display name as
  # ORCID rendered it. Some works have empty contributor blocks.
  contributors <- (w$contributors %||% list())$contributor %||% list()
  authors <- map_chr(contributors, function(c) {
    (c$`credit-name` %||% list())$value %||% NA_character_
  })
  authors <- authors[!is.na(authors) & nzchar(authors)]

  tibble(
    title    = title,
    year     = yr,
    journal  = journal,
    type     = w$type %||% "",
    doi      = doi,
    work_url = work_url,
    authors  = list(authors)
  )
}

pubs <- map_dfr(work_resps, function(r) {
  if (inherits(r, "error")) return(NULL)
  if (resp_status(r) != 200) return(NULL)
  parse_work(resp_body_json(r))
}) |>
  # Drop anything without a year (rare, makes grouping impossible)
  filter(!is.na(year)) |>
  arrange(desc(year), title)

# ---- Deduplicate -----------------------------------------------------------
# ORCID groups the same work submitted by multiple sources (manual,
# CrossRef, Scopus, ...) — but if titles differ in casing or whitespace,
# they slip through and appear twice. Collapse same-title-same-year
# duplicates, keeping the entry with the strongest link
# (DOI > work URL > none).
pubs <- pubs |>
  mutate(
    .norm = tolower(trimws(gsub("\\s+", " ", title))),
    .lnk  = ifelse(!is.na(doi) & nzchar(doi),       2L,
            ifelse(!is.na(work_url) & nzchar(work_url), 1L, 0L))
  ) |>
  group_by(.norm, year) |>
  slice_max(.lnk, n = 1, with_ties = FALSE) |>
  ungroup() |>
  select(-.norm, -.lnk) |>
  arrange(desc(year), title)

# ---- Theme classification --------------------------------------------------
# Keyword-rule classifier. First matching theme wins; "Other" is the
# catch-all (NA pattern, always last). To recategorise a paper, edit a
# pattern here — the tribble is the single source of truth.
themes <- tribble(
  ~theme,                            ~colour,   ~pattern,
  # Methods is checked first so the manifesto paper (which also matches
  # `spatial interaction` in Migration) lands here. Narrow regex by design:
  # only papers whose titles explicitly call themselves a manifesto or a
  # methodological/teaching artefact.
  "Methods & Manifestos",            "#B53A2D", "manifesto|applied geographic|course in R",
  # Explicit-title overrides at the end (^preface$, demographic case study,
  # consistency over time) hard-classify chapters whose titles are too
  # generic for keyword matching alone.
  "Migration",                       "#1F5FA8", "migration|migrant|residential mobility|spatial interaction|inter-regional|inter regional|return migration|DEMIFER|demographic.{0,20}migrat|migratory flow|population dynamic|demographic case study|consistency over time|^preface$",
  "Housing & Energy",                "#C2542D", "\\bEPC\\b|energy performance|housing|residential (?!mobility)|dwelling|net[ -]zero|building stock|carbon|wood burning|energy efficien",
  "Schools & Education",             "#4A7B5F", "school|admission|attainment|catchment|education|takeaway|childhood",
  "Transport & Mobility",            "#8B3A8F", "transport|mobility|car dependence|\\brail\\b|\\bbus\\b|travel|commuting|trip|cycling",
  "Gentrification & Neighbourhoods", "#C28F2D", "gentrification|neighbourhood|displacement|property price|house price|urban change|residential metabolism|built[ -]to[ -]rent",
  "Planning & Policy",               "#5E4B8B", "permitted development|\\bclass[ ]?E\\b|high street|town centre|\\bTCPA\\b|planning policy",
  "Climate & Health",                "#588157", "climate disadvantage|heat vulnerab|climate vulnerab|care provision|public health|wheezing|asthma|defibrillator|\\bAED\\b",
  "Smart Cities & AI",               "#006D77", "digital twin|smart cit|colouring london|\\bAI\\b|artificial intelligence|collective intelligence|machine learning|deep learning|\\bIoT\\b|mixed reality",
  "Beer & Brewing",                  "#8A6D00", "beer|brewing|brewer|\\bpub\\b|brewery",
  "Synthetic Data & Longitudinal",   "#2E5266", "synthetic|longitudinal|\\bLS\\b|census|microsimulation|cohort|interaction data|confidentiality",
  "Politics",                        "#6B2737", "\\bBNP\\b|British National Party|electoral|\\belection|political party|right[ -]wing|voting",
  "Other",                           "#6E6862", NA_character_
)

classify_one <- function(text) {
  if (is.null(text) || is.na(text) || !nzchar(text)) return("Other")
  for (i in seq_len(nrow(themes))) {
    p <- themes$pattern[i]
    if (!is.na(p) && grepl(p, text, ignore.case = TRUE, perl = TRUE)) {
      return(themes$theme[i])
    }
  }
  "Other"
}

# ---- Manual overrides ------------------------------------------------------
# Per-paper overrides for cases where the keyword rule picks the wrong
# theme. Match on DOI (preferred — stable, unique) and/or on a title
# regex (case-insensitive). Either field may be NA. The override theme
# must exist in `themes` above, otherwise the card renders with a grey
# fallback colour.
#
# To add an override: insert a new row. Find the paper's DOI in the
# rendered card's "doi:" line (or on ORCID), and the right theme name
# from the legend chip strip at the top of the page.
overrides <- tribble(
  ~match_doi,                     ~match_title,                                          ~theme,
  "10.1016/j.apgeog.2023.103116", "Re-defining [Tt]ransport for London's strategic",     "Gentrification & Neighbourhoods",
  "10.1007/978-3-031-98300-9_17", "Do Good Schools Influence Property Prices? Disentangling School and Neighbourhood Effects with Empirical Evidence from Brighton", "Housing & Energy"
)

apply_overrides <- function(df, ov) {
  if (nrow(ov) == 0) return(df)
  for (i in seq_len(nrow(ov))) {
    mask <- rep(FALSE, nrow(df))
    if (!is.na(ov$match_doi[i]) && nzchar(ov$match_doi[i])) {
      mask <- mask | (!is.na(df$doi) &
                      tolower(df$doi) == tolower(ov$match_doi[i]))
    }
    if (!is.na(ov$match_title[i]) && nzchar(ov$match_title[i])) {
      mask <- mask | grepl(ov$match_title[i], df$title,
                           ignore.case = TRUE, perl = TRUE)
    }
    df$theme[mask] <- ov$theme[i]
  }
  df
}

pubs <- pubs |>
  mutate(theme = vapply(title, classify_one, character(1))) |>
  apply_overrides(overrides) |>
  mutate(theme_colour = themes$colour[match(theme, themes$theme)])

# ---- Renderer --------------------------------------------------------------

# Format author list as "A, B, C, ..., X & Y"
fmt_authors <- function(a) {
  if (length(a) == 0) return("")
  if (length(a) == 1) return(a)
  paste0(paste(a[-length(a)], collapse = ", "), " & ", a[length(a)])
}

pub_entry <- function(row) {
  doi  <- row$doi
  url  <- row$work_url
  href <- if (!is.na(doi) && nzchar(doi))
            paste0("https://doi.org/", doi)
          else if (!is.na(url) && nzchar(url)) url
          else NA_character_

  title_node <- if (!is.na(href)) {
    a(href = href, target = "_blank", row$title)
  } else {
    span(row$title)
  }

  authors_str <- fmt_authors(row$authors[[1]])

  meta_parts <- c()
  if (nzchar(authors_str)) meta_parts <- c(meta_parts, authors_str)
  if (nzchar(row$journal)) meta_parts <- c(meta_parts, sprintf("*%s*", row$journal))

  div(class = "pub-entry",
      # CSS variable feeds the left-border colour and the theme badge;
      # data-theme is what the legend chips filter on.
      style = sprintf("--theme-colour: %s;", row$theme_colour %||% "#6E6862"),
      `data-theme` = row$theme %||% "Other",
      div(class = "pub-title", title_node),
      if (length(meta_parts) > 0)
        p(class = "pub-meta",
          HTML(paste(vapply(meta_parts, function(s) {
            # Render the italic *journal* markdown manually
            if (startsWith(s, "*") && endsWith(s, "*")) {
              sprintf('<em class="pub-journal">%s</em>',
                      substr(s, 2, nchar(s) - 1))
            } else {
              sprintf('<span class="pub-authors">%s</span>', s)
            }
          }, character(1)), collapse = ". "))),
      div(class = "pub-bottom",
        if (!is.na(doi) && nzchar(doi))
          p(class = "pub-doi",
            a(href = paste0("https://doi.org/", doi),
              target = "_blank",
              paste0("doi: ", doi))),
        span(class = "pub-theme-badge", row$theme %||% "Other")
      )
  )
}

render_year <- function(yr, df) {
  tagList(
    h2(as.character(yr)),
    div(class = "pub-year-group",
        lapply(split(df, seq_len(nrow(df))), pub_entry))
  )
}
```

::: {.lead}
**`r nrow(pubs)` publications** indexed in my ORCID record, pulled live on
every render. The full record (and any work not represented here) lives at
[ORCID 0000-0001-8036-0185](https://orcid.org/`r ORCID`); citation counts
are on [Google Scholar](https://scholar.google.co.uk/citations?user=P_sHtmkAAAAJ).
:::

[{{< fa graduation-cap >}}&nbsp;&nbsp;PhD Thesis (PDF) — *Understanding Internal Migration in Britain at the Start of the 21st Century*, 2011](https://www.dropbox.com/scl/fi/tdrym79443ho4rfbwqyuu/AdamDennettPhDThesis.pdf?rlkey=kfdm2ca8xllnh0i9vkn8p3rda&dl=1){.btn .btn-outline-secondary role="button" target="_blank"}

```{r render}
#| output: asis

# Build the legend strip — one chip per theme that's actually represented,
# plus an "All" chip that resets the filter. Counts are computed from the
# classified pubs frame so they stay in sync.
counts <- vapply(themes$theme, function(t) sum(pubs$theme == t), integer(1))

legend <- div(class = "pub-legend",
  span(class = "pub-legend-chip pub-legend-all is-active",
    style = "--theme-colour: #1A1A1A;",
    `data-theme` = "__all",
    span(class = "pub-legend-label", "All"),
    span(class = "pub-legend-count", paste0(" (", nrow(pubs), ")"))
  ),
  lapply(seq_len(nrow(themes)), function(i) {
    n <- counts[i]
    if (n == 0) return(NULL)
    span(class = "pub-legend-chip",
      style = sprintf("--theme-colour: %s;", themes$colour[i]),
      `data-theme` = themes$theme[i],
      span(class = "pub-legend-swatch"),
      span(class = "pub-legend-label", themes$theme[i]),
      span(class = "pub-legend-count", paste0(" (", n, ")"))
    )
  })
)

years_sorted <- sort(unique(pubs$year), decreasing = TRUE)
year_sections <- lapply(years_sorted, function(y) {
  render_year(y, pubs |> filter(year == y))
})

cat("\n```{=html}\n")
cat(as.character(htmltools::tagList(legend, year_sections)))
cat("\n```\n")
```

```{=html}
<script>
(function() {
  const chips   = document.querySelectorAll(".pub-legend-chip");
  const entries = document.querySelectorAll(".pub-entry");

  chips.forEach(chip => {
    chip.addEventListener("click", () => {
      const t = chip.dataset.theme;
      chips.forEach(c => c.classList.remove("is-active"));
      chip.classList.add("is-active");
      entries.forEach(e => {
        e.style.display = (t === "__all" || e.dataset.theme === t)
          ? ""
          : "none";
      });
      // Hide year groups (and their h2 heading) whose entries are now all hidden
      document.querySelectorAll(".pub-year-group").forEach(g => {
        const anyVisible = Array.from(g.querySelectorAll(".pub-entry"))
          .some(e => e.style.display !== "none");
        const heading = g.previousElementSibling;
        g.style.display = anyVisible ? "" : "none";
        if (heading && heading.tagName === "H2")
          heading.style.display = anyVisible ? "" : "none";
      });
    });
  });
})();
</script>
```

```{r untagged-audit}
#| output: asis
others <- pubs |> filter(theme == "Other") |> select(year, title) |> arrange(desc(year))
if (nrow(others) > 0) {
  cat("\n::: {.callout-tip collapse=\"true\"}\n")
  cat(sprintf("## %d untagged paper%s\n\n", nrow(others),
              if (nrow(others) == 1) "" else "s"))
  cat("These titles didn't match any keyword rule and landed in *Other*.\n")
  cat("To classify them, edit the `themes` tribble at the top of ")
  cat("`publications.qmd` — add a keyword to an existing theme or add a new one.\n\n")
  for (i in seq_len(nrow(others))) {
    cat(sprintf("- **%d** — %s\n", others$year[i], others$title[i]))
  }
  cat(":::\n\n")
}
```

::: {.callout-tip collapse="true"}
## How this page works

The page makes a single call to ORCID's public API
(`https://pub.orcid.org/v3.0/<id>/works`) to get the summary list, then
fetches each work in detail in parallel for authors and DOIs. Nothing is
manually curated — to add or correct an entry, edit it in
[ORCID](https://orcid.org/`r ORCID`) and the next render will pick it up.

The site rebuilds automatically on every push and once a day at 05:30 UTC,
so the page is never more than a day stale even when nothing else changes.
:::
