---
title: "Publications"
description: "Pulled live from my ORCID record on every render — should always be current."
toc: true
toc-depth: 2
toc-title: "Jump to year"
format:
  html:
    page-layout: full
execute:
  echo: false
  warning: false
  message: false
  freeze: false   # always re-fetch from ORCID
---

```{r setup}
library(httr2)
library(jsonlite)
library(dplyr)
library(purrr)
library(htmltools)
library(stringr)

ORCID <- "0000-0001-8036-0185"

# ---- ORCID API helpers -----------------------------------------------------

orcid_req <- function(url) {
  request(url) |>
    req_headers(Accept = "application/json",
                `User-Agent` = "adamdennett.co.uk publications page")
}

# Fetch the summary list of all works.
works_summary <- orcid_req(sprintf(
  "https://pub.orcid.org/v3.0/%s/works", ORCID
)) |>
  req_perform() |>
  resp_body_json()

groups <- works_summary$group

# ORCID groups duplicate submissions of the same work (same DOI) into one
# group with multiple work-summary entries (one per source — manual,
# CrossRef, Scopus, ...). Pick the first put-code from each group as the
# canonical entry, then fetch its full record (which has authors).
put_codes <- map_chr(groups, ~ as.character(.x$`work-summary`[[1]]$`put-code`))

work_reqs <- map(put_codes, function(pc) {
  orcid_req(sprintf("https://pub.orcid.org/v3.0/%s/work/%s", ORCID, pc))
})

work_resps <- req_perform_parallel(work_reqs, on_error = "continue",
                                   max_active = 8)

# ---- Parse one work record into a tidy row ---------------------------------

parse_work <- function(w) {
  if (is.null(w)) return(NULL)
  title <- w$title$title$value %||% NA_character_
  if (is.na(title) || !nzchar(title)) return(NULL)

  yr <- suppressWarnings(as.integer(
    (w$`publication-date` %||% list())$year$value
  ))

  journal <- (w$`journal-title` %||% list())$value %||% ""

  # External IDs — pull out DOI (preferred) or any other URL
  ext_ids <- (w$`external-ids` %||% list())$`external-id` %||% list()
  doi <- NA_character_
  for (eid in ext_ids) {
    if (identical(eid$`external-id-type`, "doi")) {
      doi <- eid$`external-id-value`; break
    }
  }

  # Work URL (often points at the publisher / DOI landing page)
  work_url <- (w$url %||% list())$value %||% NA_character_

  # Contributors (authors) — credit-name.value is the display name as
  # ORCID rendered it. Some works have empty contributor blocks.
  contributors <- (w$contributors %||% list())$contributor %||% list()
  authors <- map_chr(contributors, function(c) {
    (c$`credit-name` %||% list())$value %||% NA_character_
  })
  authors <- authors[!is.na(authors) & nzchar(authors)]

  tibble(
    title    = title,
    year     = yr,
    journal  = journal,
    type     = w$type %||% "",
    doi      = doi,
    work_url = work_url,
    authors  = list(authors)
  )
}

pubs <- map_dfr(work_resps, function(r) {
  if (inherits(r, "error")) return(NULL)
  if (resp_status(r) != 200) return(NULL)
  parse_work(resp_body_json(r))
}) |>
  # Drop anything without a year (rare, makes grouping impossible)
  filter(!is.na(year)) |>
  arrange(desc(year), title)

# ---- Renderer --------------------------------------------------------------

# Format author list as "A, B, C, ..., X & Y"
fmt_authors <- function(a) {
  if (length(a) == 0) return("")
  if (length(a) == 1) return(a)
  paste0(paste(a[-length(a)], collapse = ", "), " & ", a[length(a)])
}

pub_entry <- function(row) {
  doi  <- row$doi
  url  <- row$work_url
  href <- if (!is.na(doi) && nzchar(doi))
            paste0("https://doi.org/", doi)
          else if (!is.na(url) && nzchar(url)) url
          else NA_character_

  title_node <- if (!is.na(href)) {
    a(href = href, target = "_blank", row$title)
  } else {
    span(row$title)
  }

  authors_str <- fmt_authors(row$authors[[1]])

  meta_parts <- c()
  if (nzchar(authors_str)) meta_parts <- c(meta_parts, authors_str)
  if (nzchar(row$journal)) meta_parts <- c(meta_parts, sprintf("*%s*", row$journal))

  div(class = "pub-entry",
      div(class = "pub-title", title_node),
      if (length(meta_parts) > 0)
        p(class = "pub-meta",
          HTML(paste(vapply(meta_parts, function(s) {
            # Render the italic *journal* markdown manually
            if (startsWith(s, "*") && endsWith(s, "*")) {
              sprintf('<em class="pub-journal">%s</em>',
                      substr(s, 2, nchar(s) - 1))
            } else {
              sprintf('<span class="pub-authors">%s</span>', s)
            }
          }, character(1)), collapse = ". "))),
      if (!is.na(doi) && nzchar(doi))
        p(class = "pub-doi",
          a(href = paste0("https://doi.org/", doi),
            target = "_blank",
            paste0("doi: ", doi)))
  )
}

render_year <- function(yr, df) {
  tagList(
    h2(as.character(yr)),
    div(class = "pub-year-group",
        lapply(split(df, seq_len(nrow(df))), pub_entry))
  )
}
```

::: {.lead}
**`r nrow(pubs)` publications** indexed in my ORCID record, pulled live on
every render. The full record (and any work not represented here) lives at
[ORCID 0000-0001-8036-0185](https://orcid.org/`r ORCID`); citation counts
are on [Google Scholar](https://scholar.google.co.uk/citations?user=P_sHtmkAAAAJ).
:::

```{r render}
#| output: asis
years_sorted <- sort(unique(pubs$year), decreasing = TRUE)
sections <- lapply(years_sorted, function(y) {
  render_year(y, pubs |> filter(year == y))
})

cat("\n```{=html}\n")
cat(as.character(htmltools::tagList(sections)))
cat("\n```\n")
```

::: {.callout-tip collapse="true"}
## How this page works

The page makes a single call to ORCID's public API
(`https://pub.orcid.org/v3.0/<id>/works`) to get the summary list, then
fetches each work in detail in parallel for authors and DOIs. Nothing is
manually curated — to add or correct an entry, edit it in
[ORCID](https://orcid.org/`r ORCID`) and the next render will pick it up.

The site rebuilds automatically on every push and once a day at 05:30 UTC,
so the page is never more than a day stale even when nothing else changes.
:::
