---
name: Adam
surname: Dennett
position: "Professor of Urban Analytics"
address: "Bartlett Centre for Advanced Spatial Analysis, University College London"
email: "a.dennett@ucl.ac.uk"
www: "adamdennett.co.uk"
github: "adamdennett"
orcid: "0000-0001-8036-0185"
twitter: "adam_dennett"
profilepic: "../assets/MeCrop.jpg"
headcolor: "1F5FA8"
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    keep_tex: false
    page_total: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Profile

I am Professor of Urban Analytics at the Bartlett Centre for Advanced Spatial
Analysis (CASA), University College London. My research uses data and
quantitative methods — frequently in R — to understand cities, migration,
housing and the systems people create. I publish across migration modelling
(particularly spatial interaction models), housing and energy, gentrification,
synthetic data and the geographies of beer and brewing, and have a passion
for applied work in urban policy contexts.

# Professional History

```{r history}
tribble(
  ~start, ~end,        ~role,                                                                  ~place,
  "2021", "Present",   "Professor of Urban Analytics",                                         "Bartlett Centre for Advanced Spatial Analysis, UCL",
  "2018", "2023",      "Head of Department and Director",                                      "Bartlett Centre for Advanced Spatial Analysis, UCL",
  "2017", "2021",      "Associate Professor, Urban Analytics",                                 "Bartlett Centre for Advanced Spatial Analysis, UCL",
  "2016", "2018",      "Deputy Director",                                                      "Bartlett Centre for Advanced Spatial Analysis, UCL",
  "2013", "2017",      "Lecturer in Urban Analytics",                                          "Bartlett Centre for Advanced Spatial Analysis, UCL",
  "2010", "2013",      "Post-doctoral Research Associate",                                     "Bartlett Centre for Advanced Spatial Analysis, UCL",
  "2006", "2010",      "Research Assistant and part-time PhD student",                         "School of Geography, University of Leeds",
  "2002", "2005",      "Teacher of Geography and Head of General Studies",                     "Hedingham School, Essex"
) %>%
  detailed_entries(
    what  = place,            # awesomecv: #1 (small caps, gray, bottom line)
    when  = paste(start, end, sep = "--"),
    with  = role              # awesomecv: #2 (bold, dark, top line)
  )
```

# Education

```{r education}
tribble(
  ~start, ~end,    ~degree,                                                                 ~inst,                                                            ~note,
  "2007", "2011",  "PhD in Quantitative Human Geography",                                   "School of Geography, University of Leeds",                       "Studied part-time",
  "2005", "2006",  "MA in Human Geography with Geographic Information Systems",             "School of Geography, University of Leeds",                       "Pass with Distinction",
  "2003", "2003",  "Qualified Teacher Status (QTS)",                                        "National College of Teaching and Leadership, DfE",               NA,
  "2001", "2002",  "PGCE in Secondary Geography",                                           "Faculty of Education (Homerton College), University of Cambridge", NA,
  "1998", "2001",  "BSc (Hons) Geography",                                                  "Lancaster University",                                           NA
) %>%
  detailed_entries(
    what  = inst,             # awesomecv: #1 (small caps, gray, bottom line)
    when  = paste(start, end, sep = "--"),
    with  = degree,           # awesomecv: #2 (bold, dark, top line)
    why   = note
  )
```

# Appointments and Affiliations

```{r affiliations}
tribble(
  ~start, ~end,        ~role,                                                                              ~place,
  "2024", "Present",   "Member, ESRC Peer Review College",                                                 "ESRC",
  "2023", "Present",   "External Examiner, MSc Geographical Information Science",                          "University of Manchester",
  "2017", "2023",      "Editor-in-Chief, Applied Spatial Analysis and Policy (Impact Factor 1.9)",         "Springer",
  "2021", "Present",   "Fellow of the Academy of Social Sciences (FAcSS) — Elected",                       "Academy of Social Sciences",
  "2010", "Present",   "Fellow of the Royal Geographical Society (FRGS)",                                  "Royal Geographical Society"
) %>%
  detailed_entries(
    what  = place,            # bottom line (small caps)
    when  = paste(start, end, sep = "--"),
    with  = role              # top line (bold)
  )
```

# Prizes, Awards and Honours

```{r awards}
tribble(
  ~year,   ~award,                                                                                                ~where,
  "2025",  "Best Paper, 33rd Annual GIS Research UK (GISRUK) Conference",                                          "University of Bristol",
  "2021",  "Elected Fellow of the Academy of Social Sciences (FAcSS)",                                             "Academy of Social Sciences",
  "2020",  "Cabinet Office Geospatial Commission, Geography in Government Award — Excellence in Local Government", "Awarded with City of Westminster Council for pioneering Urban Lab work",
  "2019",  "Best Paper, 27th Annual GIS Research UK (GISRUK) Conference (Colouring London Project)",               "University of Newcastle",
  "2016",  "UCLU Student Choice Teaching Award for Outstanding Teaching",                                          "University College London",
  "2006",  "Grebenik Prize — best work on any aspect of human population problems",                                "University of Leeds"
) %>%
  detailed_entries(
    what  = where,            # bottom line (small caps)
    when  = year,
    with  = award             # top line (bold)
  )
```

# Grants

External grants total awarded as PI or Co-I since 2012: **£17,491,621.90**.

```{r grants}
tribble(
  ~start_year, ~title,                                                                                                        ~role_status,                                                       ~funder_value,
  "2024",      "Census Innovation at CeLSIUS (ES/Z502741/1)",                                                                  "Co-I; active",                                                     "£384,576",
  "2024",      "TRACK-UK: Synthesized Census and Small Area Statistics for Transport and Energy (ES/Z50290X/1)",                "Co-I; active",                                                     "£327,680",
  "2024",      "AI for Collective Intelligence (AI4CI) — UKRI AI Research Hub for Real Data (EP/Y028392/1)",                    "Co-I; Local PI for UCL branch; active",                            "£10,274,279 (UCL portion £980,391.77)",
  "2023",      "Pathways to socially equitable net-zero cities and regions — ESRC CASE PhD Studentship",                        "PI/Supervisor (Transport East partner); active",                   "£93,633.90",
  "2023",      "Equity Assessment of Demand-side Flexibility Technologies in Grid Integrated Transport Electrification (PhD)",  "PI/Supervisor (EPSRC CREDS); active",                              "£96,044",
  "2022",      "NARRATE",                                                                                                       "PI; complete",                                                     "£142,739.24 (Ordnance Survey)",
  "2020",      "dunnhumby PhD Studentship",                                                                                     "PI/Supervisor (industry-funded); complete",                        "£60,000 (dunnhumby)",
  "2020",      "CeLSIUS (ES/V003488/1)",                                                                                        "Co-I; active",                                                     "£2,160,348.40 (ESRC)",
  "2019",      "YOUR.VU.CITY (UKRI 105325)",                                                                                    "Local PI (Co-I on whole project); complete",                       "£620,697 (UCL £159,996; Innovate UK)",
  "2018",      "CeLSIUS Re-commissioning (ES/R00823X/1)",                                                                       "Co-I; complete",                                                   "£1,020,753 (ESRC)",
  "2018",      "Colouring London Impact Acceleration Grant",                                                                    "PI; complete",                                                     "£55,200 (EPSRC)",
  "2016",      "CeLSIUS Extension Grant",                                                                                       "Co-I; complete",                                                   "£247,182.40 (ESRC)",
  "2016",      "Colouring London",                                                                                              "PI (with Co-PI Polly Hudson); complete",                           "£58,400.74 (Historic England)",
  "2014",      "RGS Innovative Teaching Grant",                                                                                 "PI (Co-I Paul Turner, Bedales School); complete",                  "£1,000 (RGS)",
  "2013",      "SYLLS — Synthetic data estimation for the UK Longitudinal Studies",                                             "PI; complete",                                                     "£272,652.73 (ESRC)",
  "2012",      "CeLSIUS (ES/K000365/1)",                                                                                        "Co-I; complete",                                                   "£1,676,436 (ESRC)"
) %>%
  detailed_entries(
    what  = role_status,      # bottom line (small caps)
    when  = start_year,
    with  = title,            # top line (bold)
    why   = funder_value
  )
```

# Invited Talks (recent)

```{r talks}
tribble(
  ~when,             ~what,                                                                                                                              ~where,
  "Sept 2025",       "Smart Cities and Collective Intelligence",                                                                                          "UCL Development Planning Unit — talk to Latin American city leaders",
  "Aug 2025",        "GIS vs The City Council: Data Analytics, Collective Intelligence and Policy Dust-ups (GISRUK 2025 Best Paper)",                    "Royal Geographical Society Annual Conference",
  "March 2025",      "The Case of the Brighton Secondary School Admissions Consultation",                                                                "Brighton Data Forum (public lecture)",
  "Feb 2025",        "Data Analytics and the Brighton Secondary School Admissions debate",                                                               "Institute for Spatial Data Science, University of Leeds (departmental seminar)",
  "Jan 2025",        "Data and evidence missing from the B&H Secondary School Admissions Consultation",                                                  "Parent Support Group, Brighton (online public lecture)",
  "Dec 2024",        "Early career researcher panel, Urban Analytics meeting",                                                                            "Alan Turing Institute / University of Glasgow",
  "Sept 2024",       "Housing and Net-Zero",                                                                                                              "Aalto University, Finland",
  "Feb 2024",        "Evidence against the effects of schools on local house prices in Brighton and Hove",                                               "Geographic Data Science Lab, University of Liverpool (departmental seminar)",
  "Nov 2023",        "Foundations of Geospatial",                                                                                                          "Carto Spatial Data Science Bootcamp, London (invited back)",
  "May 2023",        "Careers panel",                                                                                                                     "Carto annual conference, Royal Geographical Society, London",
  "Feb 2023",        "Foundations of Geospatial",                                                                                                          "Carto Spatial Data Science Bootcamp, London"
) %>%
  detailed_entries(
    what  = what,
    when  = when,
    with  = where
  )
```

# PhD Supervision

## Current research students

```{r phd-current}
tribble(
  ~start_year, ~student_project,                                                                                                                                                  ~role,
  "2023",      "Maria Wood — Equity assessment of demand-side flexibility technologies in transportation decarbonisation (with Esra Suel, Gerry Casey). Upgrade passed.",          "1st supervisor",
  "2023",      "Claude Lynch — Pathways to Socially Equitable Net Zero Cities and Regions (with Esra Suel, Gerry Casey). Upgrade passed.",                                          "1st supervisor",
  "2023",      "Tom Murat — Generative scenarios for getting Transport to an equitable Net Zero (with Esra Suel, Gerry Casey).",                                                    "1st supervisor",
  "2018",      "Denise Mizzi (PT) — Small Area Estimation of Wheezing prevalence in Maltese School Children (with Jens Kandt, Nicola Shelton). Upgrade passed.",                    "1st supervisor",
  "2025",      "Roei Yosifof — Application of novel AI methods in the Digital Urban Planning domain. AI4CI Linked PhD.",                                                            "2nd supervisor",
  "2025",      "AI4CI Linked PhD (Glasgow half of Cities Theme) — candidate appointed.",                                                                                            "2nd supervisor",
  "2023",      "Chiara Gericke — Role of the Neighbourhood Food Environment in Susceptibility to Obesity (1st sup. Claire Llewellyn, Institute of Epidemiology and Health Care).",  "2nd supervisor"
) %>%
  detailed_entries(
    what  = student_project,
    when  = start_year,
    with  = role
  )
```

## Completed

```{r phd-completed}
tribble(
  ~years,            ~student_project,                                                                                                                                  ~role,
  "2020 -- 2023",    "Philip Wilkinson — Applications of novel retail modelling methodologies in an evolving grocery sector (2nd sup. Neave O'Clery). Minor corrections.", "1st supervisor",
  "2016 -- 2022",    "Bonnie Buyuklieva — Understanding London's Residential Metabolism (2nd sup. Hannah Fry). Minor corrections.",                                       "1st supervisor",
  "2016 -- 2021",    "Bin Chi — Spatial and temporal patterns of residential house prices and affordability in the UK (2nd sup. Thomas Oléron Evans). Passed without corrections.", "1st supervisor",
  "2016 -- 2020",    "Matthew Ng — The future of Brunei: changes in Brunei-Muara's urban and population landscapes (2nd sup. Elsa Arcaute). Minor corrections.",          "1st supervisor",
  "2019 -- 2024",    "Yufeng Wu — Dynamics of return migration intention and behaviour in China (1st sup. Rory Coulter).",                                                "2nd supervisor",
  "2015 -- 2016",    "Lixun Liu — Impacts of rail transit investment on development in Chongqing (1st sup. Robin Hickman). Minor corrections.",                            "2nd supervisor"
) %>%
  detailed_entries(
    what  = student_project,
    when  = years,
    with  = role
  )
```

## MSc / MRes
Supervised 45+ dissertations between 2017--2025. Joshua Yee (2019) won the
RGS-IBG Population Geography Research Group postgraduate dissertation prize.

# Research Staff Line Management

```{r staff}
tribble(
  ~years,         ~project,                                                                                       ~staff,
  "2024-Present", "AI for Collective Intelligence National Research Hub",                                          "Dr Beatrice Taylor; Adham Enaya; Dr Yahya Gamal (Glasgow — oversight)",
  "2022-2023",    "NARRATE — Ordnance Survey Housing Net Zero R&D Project",                                        "Dr Bonnie Buyuklieva (now Lecturer in Digital Humanities, UCL)",
  "2018-2020",    "Colouring London (CASA)",                                                                       "Dr Martin de Jode (now Lecturer in CASA); Maciej Ziarkowski; Dominic Humphrey (now UCL Energy Institute)",
  "2013-2014",    "SYLLS",                                                                                          "Dr Belinda Wu"
) %>%
  detailed_entries(
    what  = project,
    when  = years,
    with  = staff
  )
```

# Academic Staff Line Management

Currently line-manage 2 academic staff. As Head of Department over a 5-year
period directly line-managed (seeing several through promotions):

- 3 Professors (one successfully re-banded during period)
- 6 Associate Professors (2 promoted to Professor during period)
- 4 Lecturers (2 promoted to Associate Professor during period)

# Selected Publications (since 2020)

A full list is available via [Google Scholar](https://scholar.google.co.uk/citations?user=P_sHtmkAAAAJ&hl=en)
and [ORCID 0000-0001-8036-0185](http://orcid.org/0000-0001-8036-0185).

```{r pubs-2024-26}
tribble(
  ~year, ~authors,                                                                                                                                     ~title_venue,
  "2026", "Lynch, C.E.H., Casey, G., Suel, E., Dennett, A.",                                                                                          "Is transport modelling 'a bit of a racket'? On the role of transport planning support systems in England. *Transportation Research Interdisciplinary Perspectives* 36. doi:10.1016/j.trip.2026.101876",
  "2026", "Wood, M., Dennett, A., Casey, G., Suel, E.",                                                                                                "Car dependence in England and Wales: spatial inequalities and implications for a just transition. *Frontiers in Sustainable Cities* 7. doi:10.3389/frsc.2025.1719495",
  "2025", "Horsfall, L., Kennedy, C., Shelton, N., Taylor, J., Hurst, J.R., Loxham, M., Dennett, A., Hardelid, P.",                                    "High-resolution mapping of residential wood burning heat sources using Energy Performance Certificates. *Environment International* 201. doi:10.1016/j.envint.2025.109537",
  "2025", "Tan, J., Dennett, A.",                                                                                                                      "Do Good Schools Influence Property Prices? Disentangling School and Neighbourhood Effects with Empirical Evidence from Brighton. In *Digital-Era Urban Transformations* (CUPUM). doi:10.1007/978-3-031-98300-9_17",
  "2024", "Dennett, A., Bullock, S., Ajmeri, N., Batty, M., Black, M., Cartlidge, J., …, Williams, H.T.P.",                                            "Artificial Intelligence for Collective Intelligence: A National-Scale Research Strategy. *Knowledge Engineering Review*. doi:10.1017/S0269888924000110",
  "2024", "Buyuklieva, B., Bevilacqua, I., Dennett, A., Reades, J., Hubbard, P.",                                                                     "Life for Rent: Evolving Residential Infrastructure in London and the Rise of Built-to-Rent. *Urban Studies*. doi:10.1177/00420980241277684",
  "2024", "Suel, E., Lynch, C., Wood, M., Murat, T., Casey, G., Dennett, A.",                                                                          "Measuring transport-associated urban inequalities: Where are we and where do we go from here? *Transport Reviews*. doi:10.1080/01441647.2024.2389800",
  "2024", "Rowe, F., Lovelace, R., Dennett, A.",                                                                                                       "Spatial interaction modelling: A manifesto. In *A Research Agenda for Spatial Analysis* (Elgar). doi:10.4337/9781802203233",
  "2024", "Buyuklieva, B., Oléron-Evans, T., Bailey, N., Dennett, A.",                                                                                 "Variations in domestic energy efficiency by property, neighbourhood and local authority type. *Frontiers in Sustainability* 5. doi:10.3389/frsus.2024.1329034",
  "2024", "Gericke, C., Llewellyn, C., Burgoine, T., Dennett, A.",                                                                                     "From textbooks to takeaways: a geospatial analysis of clustering of takeaway outlets near London schools.",
) %>%
  detailed_entries(
    what  = title_venue,
    when  = year,
    with  = authors
  )
```

```{r pubs-2023}
tribble(
  ~year, ~authors,                                                                       ~title_venue,
  "2023", "Dennett, A., Gray, S., Wyszomierski, J.",                                    "From the Beer Orders to Last Orders — Legislation, Taxation and the Modern Beer Landscape of London. In *The Geography of Beer* (Springer).",
  "2023", "Yan, X., Dennett, A.",                                                       "Re-defining transport for London's strategic neighbourhoods from spatial and social perspectives. *Applied Geography*. doi:10.1016/j.apgeog.2023.103116",
  "2023", "Wu, Y., Coulter, R., Dennett, A.",                                           "Relationships between family structures and destinations of married migrants with children in China. *Applied Geography*. doi:10.1016/j.apgeog.2023.103102",
  "2023", "Liu, L., Dennett, A., Hickman, R.",                                          "Exploring the spatial differences in travel mode choice of rail transit in Chongqing. *Transportation Planning and Technology*. doi:10.1080/03081060.2023.2228301",
  "2023", "Dennett, A., Buyuklieva, B.",                                                "Transitioning the residential environment of the UK to net-zero (CASA Working Paper 233).",
  "2023", "Buyuklieva, B., Dennett, A., Bailey, N., Morley, J.",                        "Energy Efficient Homes: Social and Spatial Patterns of Residential Energy Efficiency in England. *GISRUK proceedings*. doi:10.5281/zenodo.7855112",
  "2023", "Liu, L., Dennett, A., Hickman, R.",                                          "Social equity impacts of rail transit investments using community perceptions: evidence from Chongqing. *Transportation Planning and Technology*. doi:10.1080/03081060.2022.2152454"
) %>%
  detailed_entries(
    what  = title_venue,
    when  = year,
    with  = authors
  )
```

```{r pubs-2020-22}
tribble(
  ~year, ~authors,                                                                ~title_venue,
  "2022", "MacLachlan, A., Dennett, A.",                                          "An Applied Geographic Information Systems and Science Course in R. *Journal of Open Source Education* 5(50). doi:10.21105/jose.00141",
  "2022", "Yee, J., Dennett, A.",                                                 "Stratifying and predicting patterns of neighbourhood change and gentrification: an urban analytics approach. *Transactions of the Institute of British Geographers*. doi:10.1111/tran.12522",
  "2021", "Spooner, F., Abrams, J.F., Morrissey, K., Shaddick, G., Batty, M., et al.", "A dynamic microsimulation model for epidemics. *Social Science & Medicine* 291. doi:10.1016/j.socscimed.2021.114461",
  "2021", "Chi, B., Dennett, A., Oléron-Evans, T., Morphet, R.",                  "A new attribute-linked residential property price dataset for England and Wales, 2011--2019. *UCL Open: Environment*. doi:10.14324/111.444/ucloe.000019",
  "2021", "Clifford, B., Dennett, A., Chi, B.",                                   "Mapping Class E: Understanding the expansion of permitted development. *TCPA report*.",
  "2021", "Chi, B., Dennett, A., Oléron-Evans, T., Morphet, R.",                  "Delineating the Spatio-Temporal Pattern of House Price Variation by Local Authority in England: 2009 to 2016. *Geographical Analysis*. doi:10.1111/gean.12287",
  "2020", "Chi, B., Dennett, A., Evans, T., Morphet, R.",                         "Shedding new light on residential property price variation in England: A multi-scale exploration. *Environment and Planning B*. doi:10.1177/2399808320951212"
) %>%
  detailed_entries(
    what  = title_venue,
    when  = year,
    with  = authors
  )
```
