---
title: "Teaching"
description: "Workshops, modules, and teaching resources."
listing:
  id: teaching-items
  contents: "*/index.qmd"
  type: grid
  sort: "date desc"
  categories: true
  sort-ui: false
  filter-ui: false
  fields: [image, date, title, description, categories]
  image-height: 220px
page-layout: full
title-block-banner: false
execute:
  echo: false
  warning: false
  message: false
  freeze: false   # always re-scrape RPubs in case items are added
---

::: {#teaching-items}
:::

## GitHub teaching resources

Auto-pulled from repos whose README front-matter includes `type: teaching`.

```{r github-teaching}
#| output: asis

library(httr2)
library(jsonlite)
library(dplyr)
library(purrr)
library(htmltools)
library(lubridate)
library(yaml)
library(stringr)

gh_token <- function() {
  Sys.getenv("GITHUB_PAT", unset = Sys.getenv("GITHUB_TOKEN"))
}

gh_req <- function(url) {
  req <- request(url) |>
    req_headers("Accept" = "application/vnd.github+json",
                "X-GitHub-Api-Version" = "2022-11-28") |>
    req_error(is_error = function(resp) FALSE)
  pat <- gh_token()
  if (nzchar(pat)) req <- req_auth_bearer_token(req, pat)
  req
}

fetch_repos <- function(user = "adamdennett") {
  gh_req(sprintf("https://api.github.com/users/%s/repos?per_page=100&type=owner&sort=updated", user)) |>
    req_perform() |>
    resp_body_json()
}

fetch_readme <- function(repo_full_name, default_branch) {
  url <- sprintf("https://raw.githubusercontent.com/%s/%s/README.md",
                 repo_full_name, default_branch)
  resp <- gh_req(url) |> req_perform()
  if (resp_status(resp) != 200) return(NULL)
  resp_body_string(resp)
}

split_frontmatter <- function(text) {
  if (is.null(text) || !nzchar(text)) return(list(meta = list(), body = ""))
  m <- regmatches(text,
                  regexec("(?s)^---[ \t]*\r?\n(.*?)\r?\n---[ \t]*\r?\n(.*)$",
                          text, perl = TRUE))[[1]]
  if (length(m) < 3) return(list(meta = list(), body = text))
  meta <- tryCatch(yaml::yaml.load(m[2]), error = function(e) list())
  if (!is.list(meta)) meta <- list()
  list(meta = meta, body = m[3])
}

first_image_in_body <- function(body) {
  if (!nzchar(body)) return(NULL)
  m <- regmatches(body, regexec("(?s)!\\[[^\\]]*\\]\\(([^)\\s]+)",
                                body, perl = TRUE))[[1]]
  if (length(m) >= 2) m[2] else NULL
}

absolutize_image <- function(image, repo_full_name, default_branch) {
  if (is.null(image) || !nzchar(image)) return(NA_character_)
  if (grepl("^https?://github\\.com/[^/]+/[^/]+/blob/", image)) {
    return(sub("^https?://github\\.com/([^/]+)/([^/]+)/blob/",
               "https://raw.githubusercontent.com/\\1/\\2/", image))
  }
  if (grepl("^https?://", image)) return(image)
  image <- sub("^\\./", "", image)
  sprintf("https://raw.githubusercontent.com/%s/%s/%s",
          repo_full_name, default_branch, image)
}

repos <- fetch_repos()

base_df <- map_dfr(repos, function(r) {
  tibble(
    name           = r$name,
    full_name      = r$full_name,
    default_branch = r$default_branch %||% "main",
    description    = r$description %||% "",
    has_pages      = isTRUE(r$has_pages),
    archived       = isTRUE(r$archived),
    updated        = as_date(ymd_hms(r$updated_at)),
    repo_url       = r$html_url,
    pages_root     = sprintf("https://adamdennett.github.io/%s/", r$name)
  )
}) |>
  filter(has_pages, !archived) |>
  arrange(desc(updated))

enrich <- function(name, full_name, default_branch) {
  readme <- tryCatch(fetch_readme(full_name, default_branch), error = function(e) NULL)
  if (is.null(readme)) {
    return(tibble(meta_title = NA_character_, meta_description = NA_character_,
                  meta_site = NA_character_, meta_image = NA_character_,
                  meta_type = NA_character_))
  }
  parts <- split_frontmatter(readme)
  meta <- parts$meta
  img <- meta$image %||% first_image_in_body(parts$body)
  tibble(
    meta_title       = meta$title       %||% NA_character_,
    meta_description = meta$description %||% NA_character_,
    meta_site        = meta$site        %||% NA_character_,
    meta_image       = absolutize_image(img, full_name, default_branch),
    meta_type        = tolower(trimws(meta$type %||% NA_character_))
  )
}

enriched <- pmap_dfr(
  list(base_df$name, base_df$full_name, base_df$default_branch),
  enrich
)

teaching_df <- bind_cols(base_df, enriched) |>
  filter(!is.na(meta_type) & meta_type == "teaching") |>
  mutate(
    display_title       = coalesce(meta_title, name),
    display_description = coalesce(na_if(meta_description, ""), na_if(description, "")),
    pages_url           = ifelse(!is.na(meta_site) & nzchar(meta_site),
                                 paste0(pages_root, sub("^/", "", meta_site)),
                                 pages_root),
    image_url           = meta_image
  )

if (nrow(teaching_df) > 0) {
  card <- function(row) {
    has_image <- !is.na(row$image_url) && nzchar(row$image_url)
    has_desc  <- !is.na(row$display_description) && nzchar(row$display_description)

    image_block <- if (has_image) {
      a(href = row$pages_url, target = "_blank", class = "project-image-link",
        tags$img(src = row$image_url, alt = row$display_title,
                 loading = "lazy", class = "project-image"))
    }

    div(class = paste("project-card", if (has_image) "with-image" else "no-image"),
        image_block,
        div(class = "project-card-body",
            h3(class = "project-title",
               a(href = row$pages_url, target = "_blank", row$display_title)),
            if (has_desc)
              p(class = "project-desc", row$display_description)
            else
              p(class = "project-desc project-desc-empty", em("(no description)")),
            div(class = "project-meta",
                span(class = "badge date",
                     paste0("Updated ", format(row$updated, "%b %Y")))
            ),
            div(class = "project-links",
                a(href = row$pages_url, target = "_blank", "Live site →"),
                a(href = row$repo_url,  target = "_blank", "Source")
            )
        )
    )
  }

  cards <- lapply(split(teaching_df, seq_len(nrow(teaching_df))), card)

  cat("\n```{=html}\n")
  cat(as.character(div(class = "project-grid", cards)))
  cat("\n```\n")
} else {
  cat("\n*No GitHub repos tagged `type: teaching` found.*\n")
}
```

## RPubs archive

Older R Markdown documents published on [RPubs](https://rpubs.com/adam_dennett),
mostly practical notes and lecture supplements from 2014–2018 — scraped live
from my RPubs profile so the list stays current if I post anything new.

```{r rpubs}
#| output: asis

library(httr2)
library(stringr)
library(htmltools)
library(dplyr)
library(purrr)

# Decode the handful of HTML entities that appear in attribute values
# (mainly &amp; in thumbnail URLs).
unescape_html <- function(x) {
  if (is.na(x)) return(x)
  x |>
    str_replace_all("&amp;",  "&") |>
    str_replace_all("&quot;", "\"") |>
    str_replace_all("&#39;",  "'") |>
    str_replace_all("&lt;",   "<") |>
    str_replace_all("&gt;",   ">")
}

raw <- tryCatch(
  request("https://rpubs.com/adam_dennett") |>
    req_user_agent("adamdennett.co.uk teaching page") |>
    req_perform() |>
    resp_body_string(),
  error = function(e) NULL
)

if (is.null(raw)) {
  cat("\n*Couldn't reach RPubs to fetch the archive — try the ",
      "[profile page directly](https://rpubs.com/adam_dennett).*\n")
} else {
  # Each publication is wrapped in <div class="pubtile"> ... </div>.
  # Split on the opening tag (drop the first chunk before any tile).
  tiles <- str_split(raw, '<div class="pubtile">', simplify = FALSE)[[1]][-1]

  rpubs <- map_dfr(tiles, function(t) {
    url   <- str_match(t, '<h5>\\s*<a href="(https://rpubs\\.com/adam_dennett/[0-9]+)"')[,2]
    title <- str_match(t, '<h5>\\s*<a href="[^"]+">([^<]+)</a>')[,2]
    thumb <- str_match(t, 'class="pubthumb"[^>]*src="([^"]+)"')[,2]
    dt    <- str_match(t, '<time datetime="([^"]+)"')[,2]
    tibble(url = url, title = unescape_html(title),
           thumb = unescape_html(thumb),
           date = suppressWarnings(as.Date(dt)))
  }) |>
    filter(!is.na(url)) |>
    arrange(desc(date))

  if (nrow(rpubs) == 0) {
    cat("\n*No RPubs documents found in the profile.*\n")
  } else {
    cards <- lapply(seq_len(nrow(rpubs)), function(i) {
      r <- rpubs[i, ]
      has_thumb <- !is.na(r$thumb) && nzchar(r$thumb)
      div(class = "project-card with-image",
        if (has_thumb) {
          a(href = r$url, target = "_blank", class = "project-image-link",
            tags$img(src = r$thumb, alt = r$title,
                     loading = "lazy", class = "project-image"))
        },
        div(class = "project-card-body",
          h3(class = "project-title",
             a(href = r$url, target = "_blank", r$title)),
          div(class = "project-meta",
              span(class = "badge date",
                   if (!is.na(r$date)) format(r$date, "%b %Y") else "—"),
              span(class = "badge lang", "RPubs")
          ),
          div(class = "project-links",
              a(href = r$url, target = "_blank", "Open →")
          )
        )
      )
    })

    cat("\n```{=html}\n")
    cat(as.character(div(class = "project-grid", cards)))
    cat("\n```\n")
  }
}
```
